---
title: "Comics"
author: "rishabh"
output:
  pdf_document: default
  html_document: default
---
## **GGPLOT Practice Excercise** ##

1.Print the first rows of the data 
```{r}
r1 <- read.csv("Comics_Data.csv")
r1[1,]
names(r1)
```

2.Check Levels of Align Variable
```{r}
r2 <- r1[ ,c("align")] 
levels(r2)
```

3.Check Levels of Gender
```{r}
r3 <- r1[ ,c("gender")] 
levels(r3)
```

4.Create a 2 way table using align and gender
```{r}
table(r1$align, r1$gender)
```

5.Remove 'Reformed Criminals' level from align variable using dplyr
```{r}
library(dplyr)
r4 <- factor(droplevels(r2, "Reformed Criminals"))
head(r4)
```

6.Create a side by side bar chart of gender by align variable using ggplot
```{r}
library(ggplot2)
ggplot(r1, aes(x = gender, fill = align)) + geom_bar(position = "dodge") 
```

7.Create a side by side bar chart of alignment by gender using ggplot
```{r}
ggplot(r1, aes(x = align, fill = gender)) + geom_bar(position = "dodge") 
```

8.Write the interpretation of bar charts

1. There is an association between Gender and Alignment.
2. There are less number of female characters than that of male        characters.
3. bad alignment is less in female.
4. The Characters with Neutral alignment, Males are the most common.

9.Create a table of number of comics using align variable
```{r}
r5 <- table(r1$align)
r5
```

10.Create a propotional table using the above table using prop.table(), what is the proportion of Bad, Good and Neutral
```{r}
r6 <- table(r1$align)
prop.table(r6)
```

11.Create a propotional table using the above table using prop.table(), what is the proportion of No Dual, Public, Secret and Unknown
```{r}
r7 <- table(r1$id)
prop.table(r7)

```

12. Plot the proportions using ggplot(use bar plot); x = id, y = proportion, fill = align
```{r}
ggplot(data = r1, aes(x = id, fill = align)) + geom_bar(position = "fill")

```

13. Plot same as above, swap the id and align variable
```{r}
ggplot(data = r1, aes(x = align, fill = id)) + geom_bar(position = "fill")

```

14. Using proportions, answer approximately what proportion of all female 
characters are good
```{r}
r8 <- table(r1$align, r1$gender)
prop.table(r8, 2)
```
Answer = 50%

15. Plot the count of gender using align (use ggplot with bar)
```{r}
ggplot(r1, aes(x = align, fill = gender)) + geom_bar()
```

16. Plot the above plot using proportions
```{r}
ggplot(r1, aes(x = align, fill = gender)) + geom_bar(position = "fill")
```

17. Plot the distribution of id variable
```{r}
ggplot(r1, aes(x = id)) + geom_bar()
```

18. Using ggplot show the distribution of id variable, use facets to show the distribution for Bad, Good and Netural (Align Variable)
```{r}
ggplot(r1, aes(x = id)) + geom_bar() + facet_wrap(~ align)
```

19. Realgin the levels of align to show the plot as Bad, Netural and Good instead of Bad, Good and Neutral
```{r}
levels(r4)
r9 <- factor(r1, levels = c("Bad", "Good", "Neutral"), labels = c("Bad", "Neutral", "Good"), exclude = NA)
head(r9)
```

20. Make a facet plot of alignment broken down by gender
```{r}
ggplot(r1, aes(x = align)) + geom_bar() + facet_wrap(~ gender)

```

